Trends of SDR in Thessaloniki

### 2023-06-29 Article.Rmd
Commit 2023-06-29 10:17

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on the Earth's energy budget, the mechanisms of climate change, and water and carbon cycle [@Wild2009].
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world and for different time periods, using the term 'brightening' for positive trends, and 'dimming' for negative trends.
There are many cases on the long term records, showing a change of SDR trends direction, occurring roughly at the last decades of the 20th century.
<!-- Trends -->
@Yang2021 reports a general dimming before 2000 and a brightening afterwards on multiple station in China. 
@Wild2021 shows a similar pattern, with the breaking point around 1980 from a 71 years record of a Central Europe station and for Brazil by @Yamasoe2021.
<!-- @Yamasoe2021 similar dimming and brightening around 1980 in Brazil -->
@Yuan2021 with AI aided spatial analysis on continent level, containing numerous observational station, reach similar conclusions for the above regions and the global trend.

Although, there is a consensus, among researchers, that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds.

@@

>>>>

The shortwave downward solar irradiance (SDR) at the Earth's surface plays a significant role, on Earths climate.
Changes of the SDR can be related to major changes on the Earth's energy budget, the mechanisms of climate change, and water and carbon cycle [@Wild2009].
Studies of SDR variability, have identified some distinct SDR trends on different regions of the world and for different time periods, using the term 'brightening' for positive trends, and 'dimming' for negative trends.
There are many cases on the long term records, showing a change of SDR trends direction, occurring roughly at the last decades of the 20th century.
<!-- Trends -->
@Yang2021 reports a general dimming before 2000 and a brightening afterwards on multiple station in China. 
@Wild2021 shows a similar pattern, with the breaking point around 1980 from a 71 years record of a Central Europe station and for Brazil by @Yamasoe2021.
<!-- @Yamasoe2021 similar dimming and brightening around 1980 in Brazil -->
Another approach, using AI aided spatial analysis on continent level, of numerous observational stations data, reach similar conclusions for the above regions and the global trend [@Yuan2021].

There is a consensus, among researchers, that the major factors of the attenuation of SDR is the interaction with the atmospheric aerosols and the clouds.

@@

There is a also a need to evalutate the trends on different location
